A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-07-28 tex/paper.tex
not picking up cov

$\vP$ & $\{\Cheb, \Cov \}$, the collection of all nuisance parameters \\
$\vT$ & $\{\vT, \vP\}$, the collection of all parameters \\
$\vD$ & data spectrum \\
$\vM$ & model, a function of the above stellar, Chebyshev, and covariance (hyper)parameters \\
$\vR$ & $\vD - \vM $, residuals  \\
$\vC$ & covariance matrix, a function of the covariance hyper-parameters\\
$\vC_{ij}$ & an individual element in the covariance matrix\\
$r(\lambda_i, \lambda_j)$ & radial distance in wavelength space corresponding to $\Delta v$\\

>>>>

$\vP$ & $\{\Cheb, \Cov \}$, the collection of all nuisance parameters \\
$\vT$ & the collection of all stellar parameters \\
$\vD$ & data spectrum \\
$\vM$ & model, a function of the above stellar, Chebyshev, and covariance (hyper)parameters \\
$\vR$ & $\vD - \vM $, residuals  \\
$\vC$ & covariance matrix, a function of the covariance hyper-parameters\\
$\vC_{ij}$ & an individual element in the covariance matrix\\
$r(\lambda_i, \lambda_j)$ & radial distance in wavelength space corresponding to $\Delta v$\\
